---
title: "Assignment b1"
output: github_document
date: "2023-11-03"
---
# Initial Steps 

First, we need to load our dataset and the necessary packagse.
```{r}
library(datateachr) # contains data that will be used for the assignment
library(tidyverse) #includes the dplyr package for data processing and handling
library(ggplot2)
library (testthat)

```


# Exercise 1: Make a Function

I chose to make a function for a plot that I used frequently for STAT545A Mini Data Analysis Project. This function creates a jitter plot looking at the relationship between two variables within the dataset. One variable is categorical and the other is numeric.
```{r}
jitterplot <- function(x, y) {
  if (!(is.character(x))){
    stop('You have not indicated a categorical variable')
  }
  if(!(is.numeric(y))) {
    stop('You have not indicated a numeric variable.')
  }
  ggplot(mapping = aes(x, y)) + 
  geom_jitter(size = 0.8, alpha = 0.5, width = 0.1) 
}

```

# Exercise 2: Document your Function


```{r}
jitterplot <- function(x, y) {
  if (!(is.character(x))){
    stop('You have not indicated a categorical variable')
  }
  if(!(is.numeric(y))) {
    stop('You have not indicated a numeric variable.')
  }
  ggplot(mapping = aes(x, y)) + 
  geom_jitter(size = 0.8, alpha = 0.5, width = 0.1) 
}

#'@title Jitterplot
#'@description This function can be used to create a jitter plot to look at the relationship between two variables, one categorical and one numeric. The data points are of size 0.8 with alpha transparency and a set width of 0.1 so the points don't jitter too far away from one another.
#'@param x A categorical variable in the dataset, usually an independent variable.
#'@param y A numerical variable in the dataset, usually a dependent variable.
#'@return The ultimate plot that is seen is a jitter plot that shows each datapoint, using a categorical variable on the x axis and a numerical one on the y axis. This plot also allows the visualization of the mean of the numerical variable plotted.
```
# Exercise 3: Include Examples

Example 1: Plotting the relationship of the mean radius size of nuclei depending on malignancy.

```{r}
summary(cancer_sample) #shows me the variables in the dataset
```

```{r}
jitterplot(cancer_sample$diagnosis, cancer_sample$radius_mean)
```
Example 2: Plotting the relationship between tree diameter and presence of root barrier.
```{r}
summary(vancouver_trees) #shows me the variables in the dataset
```
```{r}
jitterplot(vancouver_trees$root_barrier, vancouver_trees$diameter)
```
Example 3: Plotting the relationship between the property type and the number of storeys.

```{r}
summary(apt_buildings) #shows me the variables in the dataset
```
```{r}
jitterplot(apt_buildings$property_type, apt_buildings$no_of_storeys)
```

# Exercise 4

```{r}
test_that('X not a character',{
  expect_error(jitterplot(vancouver_tree$latitude, vancouver_tree$longitude))
})

```

```{r}
test_that('Y not a numeric',{
  expect_error(jitterplot(vancouver_tree$latitude, vancouver_tree$species_name))
})

```
```{r}
test_that('Function creates a ggplot', {
  expect_is(jitterplot(cancer_sample$diagnosis, cancer_sample$radius_mean), "ggplot")
})

```
```{r}
test_that('Function cannot plot two numerical variables', {
  expect_error(jitterplot(cancer_sample$fractal_dimension_mean, cancer_sample$radius_mean))
}) #This is to test whether the function would still make a plot if there were two numerical variables.

```


